### 2020-06-28 Report/aws_325ghz_study.tex
A first complete version!?

\thispagestyle{empty}
\noindent
\textbf{\Large Study to support the definition of Arctic Weather \vspace{1mm}\\
Satellite (AWS) high frequency channels} \vspace{8mm}\\
{\bf Patrick Eriksson, Inderpreet Kaur and Simon Pfreundschuh}\\
Department of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden\vspace{10mm}

\section*{Summary}
%
The main objective of this study is to demonstrate that channels around
325\,GHz can provide a basis for cloud filtering/correction of data measured
around 183\,GHz. Previously, it was suggested that a channel at 229\,GHz to be
used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
Sounder (MWS) and will be used for cloud filtering of 183\,GHz insde that
mission. In this study, we investigate the possibility to use the 325\,GHz
channels instead. The cloud impact of high altitude cirrus clouds is
considerably higher in 325\,GHz and this makes it possible to estimate the weak
cloud impact at 183 GHz with relatively good accuracy.

On basis of the weighting functions of 183\,GHz, three specfications for
325\,GHz channels were suggested. A channel specific simple regression was
tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
The advantage of this approach is that for each 183\,GHz the cloud adjustment
can be quantified simply through a polynomial fit between the the cloud impact
in 183\,GHz channel of concern and brightness temperature differences between
183\,GHz and 325\,GHz. A similar regression scheme based on 229\,GHz was also
examined, but gave poor results. One drawback of the simple correction scheme
is its channel specific approach, which cannot benefit from the other 325\,GHz
channels available. In order to effectively use information from all 325\,GHz
channels, we suggested a machine learning based approach for cloud correction.
We used QRNN (Quantile Regression Neural Network) to to correct the cloud
impact in each 183\,GHz channel using measurements from all available channels
of 325\,GHz. All three options of 325\,GHz were evaluated, and the performance
was comparable. For some channels, interestingly, the spread of errors was
narrower than the noise of the target 183\,GHz channel. Another advantage of
using QRNN is that the cloud free values are predicted at different quantile
levels, which helps in quantifying the case-specific uncertainty estimate. A
similar QRNN model with 229\,GHz gave poor results. No critical dependency to
the 325\,GHz receiver noise temperature was observed.

This study shows that combining measurements from 325\,GHz can provide a better
cloud correction performance than 229\,GHz, and also with minimal rejection of
data. The clear-sky predictions have error distributions which are symmetric
with low bias and spread. Therefore, the NWP and standalone 1DVAR models that
utilize the ``clear-sky'' data can greatly benefit from it. Also, in data
assimilation systems, the case-specific uncertainty allows an effective
selection of weights, thus significantly improving the impact of measurements.
Another advantage of combining 183\,GHz and 325\,GHz for cloud correction is
that NWP systems, which are not yet prepared for 325 GHz, could still benefit
from the data early on.

The cloud correction analysis did not give a clear value on the relative merit
of the suggested channel options and also the measurements' degree of freedom
(DOF) was assessed based on the performed simulations. The DoF can be seen as a
measure of the effective number of channels. The DOF analysis gave further
support for selecting 325\,GHz in favour of 229\,GHz. The DOF of the 325\,GHz
options is higher or equal to the 229\,Ghz one already in clear-sky
conditions, while  for cloud conditions 325\,GHz consistently gives two
additional degrees of freedom. That is, 325\,GHz clearly gives more rich
informaion in cloudy conditions than 229\,GHz.

\setcounter{tocdepth}{1} 
\tableofcontents

\newpage
\setcounter{page}{1}

@@

In this report, the task is defined in a somewhat different manner. The aim is
not just to estimate the cloud impact, but also to investigate to which degree
the cloud impact can be removed, i.e.\ to make a cloud correction. Further, in
this report only schemes that can be based directly on AWS data will be
considered and versions involving ``B-O tests'' are left for possible future
studies. On the other hand, cloud correction of all AWS 183\,GHz channels are
investigated. Another important difference is that our simulations aim to be a
random sample of real situations, while the simulations of
\citet{rekha2012potential} have a strong over-representation of cloudy
cases.

@@

The selected threshold value is towards the high side of the ones considered by 
\citet{rekha2012potential}. A lower value improves the removal of ``cloudy'' cases,
but the fraction of incorrectly removed ``clear'' cases increases quickly. For
example, a threshold of 3\,K decreases the miss-classification of ``cloudy''
cases to 0.6\%, but increases the miss-classification for ``clear'' cases to 77\%.
If 183\,$\pm$7\,GHz is classified as cloudy, we assume that also the data from
other 183\,GHz channels are rejected.

@@

For simplicity, the frequency variation of all channel responses is assumed to
be rectangular. This selection shall not be interpreted as any opinion on the
optimal shape of these responses; a significant deviation from a rectangular
shape should be of no concern as long as the actual shape is well
characterized.

@@

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresented in the results.

\section{Overview of the 183, 229 and 325\,GHz bands}
\label{sec:overview}
% 
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$ (deviation from nadir). No hydrometeors are included. For simpler
interpretation of the results, the reflectivity is set to have no frequency
variation, i.e.\ the same value is applied for all bands. The reflectivity is
varied between 0 and 0.5 (these fixed values are only applied in this section,
the bulk simulations are using TESSEM and TELSEM for seting the surface
properties). In the figures covering transmissivities and Jacobians, the
specifications of ICI is applied for 325\,GHz channels
(Table~\ref{tab:fixed:chs}).

@@

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a three 325\,GHz channels option. The
    values in the three last columns is the 1$\sigma$ noise level according to
    Eq.~\ref{eq:noise}, for $T_a=300$\,K and stated $T_r$ }
  \label{tab:chs:prel3}
\end{table}

@@

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-42  & 325.15$\pm$3.30 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{The second three channel suggestion.}
  \label{tab:chs:3b}
\end{table}

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
      against cloud impact in AWS-34. Red and green colour represent the clear
      and cloudy cases respectively in the simulation dataset. The black curve
      represents the line of best fit (of green points) as a third order
      polynomial. The blue vertical line represents the correction threshold,
      $x_{cs}$, for $dtb_{cs} =$ 0.2\,K. }
	\label{fig:fit:c34-42}
\end{figure}
%

@@

Figure~\ref{fig:correction:c34-42:thinned} shows the deviation of the uncorrected and
corrected measurements to their noise-free clear-sky values for the thinned dataset. The results from \cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to allow a more direct comparison of our
approach with \cite{rekha2012potential}, we also include the
dataset, ``Filtered'', where all cloudy cases are rejected. Apart from the fit
based cloudy classification, it is also assumed that cases with $Tb2-Tb1 < $
-15\,K are ``too-cloudy'' and are rejected.  To analyse the sensitivity of our scheme to noise threhold, as discussed in the previous section, results from two different values of $dtb_{cs}$ are shown. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
($x_{cs}$) is calculated using Eq~\ref{eq:dtb}. Various metrics corresponding to
the Figure~\ref{fig:correction:c34-42:thinned} are shown in
Table~\ref{tab:correction:stats:34:42:thinned}.

@@

\subsection{QRNN model}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimize the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimize the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).

@@

\subsubsection{Training}
%  
\label{sec:qrnn:training}
\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$). Here QRNN is trained to predict clear-sky values for AWS-34 using four channels option of 325\,GHz}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs measurements from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is measurements from all channels of 325\,GHz and measurements from the 183\,GHz to be predicted. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two suggestions for three channel option are described in Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

To develop the QRNN based correction scheme, we use the same dataset as in the
simple scheme . Out of 125\,000 simulations, 90\% are used to train the model,
while the rest 10\% is used to evaluate the model's performance during
training. Presently we train QRNN for only nadir sensor viewing angle and the
receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the
input according to Eq.~\ref{eq:noise}, every time the training data are exposed
to the model. This ensures that the model is exposed to a new dataset on every
iteration. Before training, the input data is normalized with mean and standard
deviation.

@@

The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. For QRNN models presented here, we did not optimize the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 256 samples for all QRNN models.

@@

The distributions of the predicted clear-sky noise-free values for each of the
183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}. The simulated
clear-sky distributions are also plotted for reference. These results are from
the four channel option. The distributions show that QRNN is overall successful in
predicting the clear-sky cases. For all channels, the simulations and
predictions have a good agreement for the main peak of the distribution.
However, for AWS-32, AWS-33 and AWS-34, QRNN seems to predict slightly colder
TBs. These results give an indication of the behavior of QRNN, but for a
detailed analysis of the prediction accuracy, we make a quantitative assessment
of the errors.

@@

For AWS-35 (Table~\ref{tab:qrnn:C35}), the four channels option has the best performance. The average bias in QRNN predictions (four) is only 0.04\,K in comparsion to -0.42\,K for the measurements. Option ``three-b'' has lower skewness than option four, but the standard deviation is higher. It is interesting to note that the standard deviation in all three predicted datasets is always lower than noise. Similar results are also seen for AWS-36 (Table~\ref{tab:qrnn:C36}). The four channels combination reduces the average bias from -0.269\,K to 0.056\,K and the standard deviation from 2.059\,K to 0.779\,K. Also for this channel, the spread of the predictions is narrower than noise.

@@

The average deviation of the uncorrected measurements to noise-free clear-sky
simulations is -1.343\,K and the standard deviation is 5.908\,K. When trained
with AWS-4X, the predictions are not very successful in alleviating the cloud
impact. Although, the error standard deviation of the predicted dataset is
lower, a large negative skewness (-4.085) indicates significantly high
uncorrected cloud impact. On the other hand, QRNN predictions trained with
325\,GHz data are also not completely cloud free, but have a slightly better
accuracy. The error standard deviation for the four channels option is
0.878\,K.

Clearly, without additional information, QRNN cannot learn to predict cloud free values for AWS-32.
As already seen in simple correction scheme, AWS-4X is not sufficient enough to characterize the effect of hydrometeors in AWS-32.

@@

\section{Degrees of freedom}
%
The information content analysis in the AWS is made by estimating the degrees of freedom (DoF) of the simulated measurements. The analysis is similar to the one described by  \citet{eriksson:towar:20} for ICI.

@@

\begin{equation}
\mathbf{S_y = E \Lambda E^T} 
\end{equation}

Similarly, the uncertainty due to thermal noise is
\begin{equation}
\mathbf{S_{\Lambda} = E S_{\epsilon} E^T }
\end{equation}

where, $\mathbf{S_{\epsilon}}$ is a diagonal matrix with NE$\Delta$T$^2$ as diagonal elements. The DoF is the number of diagonal elements of $\mathbf{\Lambda}$ greater than the $\mathbf{S_\Lambda}$. For further details see \citet{eriksson:towar:20}.

To calculate the DoF, the ensemble of simulations from 89\,GHz, 166\,GHz, 183\,GHz are used along with 229\,GHz or 325\,GHz. All three options of 325\,GHz are considered. In this section, a new suggestion of option-3b is considered. The new option is mentioned in Table~\ref{tab:option3b:new}.

In order to compare the DoF for cloudy and clear cases, we divide the database into three parts: ``all'', ``clear'' and ``cloudy'. All cases with cloud impact greater than 1\,K in any of the 183\,GHz channels are classfied as ``cloudy'', otherwise they are classified as ``clear''. With this criteria, out of total 125460 cases, 12905 are classified as cloudy.

Fig~\ref{fig:DoF:clear:1200K} shows the ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.

Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are considered. For $T_r$ = 1200\,K, the DoF from all three options is around 8, however, increase in receiver noise leads to a loss in the DoF. For $T_r$ = 2400\,K, the DoF for option three-a is 7.8, while for three-b and four, the DoF is 7.7 and 6.2 respectively. Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for clear-sky and cloudy cases respectively. For clear-sky situations, the DoF for option three-a and three-b is 7.3 and 7 respectively, while for option 4 it is 7. With increase in $T_r$, the weaker DoF are degraded. For $T_r$ = 2400\,K, we have only 5 DoF for option three-a and 4.8 for both option three-b and 4.9 for option four. On the other hand, the presence of clouds increases the DoF significantly. For all three options, we have DoF around 8. Increase in noise has no significant effect on the DoF for cloudy cases.

The channels of 325\,GHz are highly correlated with 183\,GHz for clear-sky conditions, thus there is a high redundancy in information between these two channels. Due to redundancy with 183\,GHz channel, we observe a reduction in the DoF for clear-sky conditions. However in cloudy situations, as the impact of clouds in 325\,GHz is higher, we observe a larger DoF.

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
&	325\,GHz & \multicolumn{3}{c}{DoF}   \\
&	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
\hline
			all &	four   &              8.2 &              7.8 &              6.2 \\
				& four-a   &              8.3 &              8.0   &              6.1 \\

>>>>

% \thispagestyle{empty}
\pagenumbering{roman}

\noindent
\textbf{\Large Study to support the definition of Arctic Weather \vspace{1mm}\\
Satellite (AWS) high frequency channels} \vspace{8mm}\\
{\bf Patrick Eriksson, Inderpreet Kaur and Simon Pfreundschuh}\\
Department of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden\vspace{10mm}

\section*{Summary}
%
The main objective of this study is to demonstrate that channels around
325\,GHz can provide a basis for cloud filtering/correction of data measured
around 183\,GHz. Previously, it was suggested that a channel at 229\,GHz to be
used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
Sounder (MWS) and will be used for cloud filtering of 183\,GHz inside that
mission. In this study, we investigate the possibility to use the 325\,GHz
channels instead. The cloud impact of high altitude cirrus clouds is
considerably higher in 325\,GHz and this makes it possible to estimate the weak
cloud impact at 183 GHz with relatively good accuracy.

On basis of the weighting functions of 183\,GHz, three specifications for
325\,GHz channels were suggested. A channel specific simple regression was
tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
The advantage of this approach is that for each 183\,GHz the cloud adjustment
can be quantified simply through a polynomial fit between the the cloud impact
in 183\,GHz channel of concern and brightness temperature differences between
183\,GHz and 325\,GHz. A similar regression scheme based on 229\,GHz was also
examined, but gave poor results. One drawback of the simple correction scheme
is its channel specific approach, which cannot benefit from the other 325\,GHz
channels available. In order to effectively use information from all 325\,GHz
channels, we suggested a machine learning based approach for cloud correction.
We used QRNN (Quantile Regression Neural Network) to to correct the cloud
impact in each 183\,GHz channel using measurements from all available channels
of 325\,GHz. All three options of 325\,GHz were evaluated, and the performance
was comparable. For some channels, interestingly, the spread of errors was
narrower than the noise of the target 183\,GHz channel. Another advantage of
using QRNN is that the cloud free values are predicted at different quantile
levels, which helps in quantifying the case-specific uncertainty estimate. A
similar QRNN model with 229\,GHz gave poor results. No critical dependency to
the 325\,GHz receiver noise temperature was observed.

This study shows that combining measurements from 325\,GHz can provide a better
cloud correction performance than 229\,GHz, and also with minimal rejection of
data. The clear-sky predictions have error distributions which are symmetric
with low bias and spread. Therefore, the NWP and standalone 1DVAR models that
utilise the ``clear-sky'' data can greatly benefit from it. Also, in data
assimilation systems, the case-specific uncertainty allows an effective
selection of weights, thus significantly improving the impact of measurements.
Another advantage of combining 183\,GHz and 325\,GHz for cloud correction is
that NWP systems, which are not yet prepared for 325 GHz, could still benefit
from the data early on.

The cloud correction analysis did not give a clear value on the relative merit
of the suggested channel options and also the measurements' degree of freedom
(DoF) was assessed based on the performed simulations. The DoF can be seen as a
measure of the effective number of channels. The DoF analysis gave further
support for selecting 325\,GHz in favour of 229\,GHz. The DoF of the 325\,GHz
options is higher or equal to the 229\,GHz one already in clear-sky conditions,
while for cloud conditions 325\,GHz consistently gives two additional degrees
of freedom. Some additional 325\,GHz channel versions were considered in the DoF
analysis.

With 325\,GHz as a better option confirmed, the next step is to establish
requirements for these channels. The study considered this question to some
extent. The cloud correction simulations gave no clear constraints on the
requirements, while the DoF analysis at least gave some indications. By
comparison to the NE$\Delta$D requirements for ICI and DoF values derived, it
is suggested to set threshold, target and breakthrough for the 325\,GHz
receiver noise temperature to 2400, 1800 and 1200\,K, respectively. Regarding
number, position and widths of channels, the differences between considered
options are relatively small and at this point it seems reasonable to let
technical considerations guide the basic selection between having three or four
channels. Later, when the technical constraints (such as the IF range
available) are better known an updated assessment should be performed to set
the final channel values.

\vspace{10mm}
\setcounter{tocdepth}{1} 
\tableofcontents

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}

@@

In this report, the task is defined in a somewhat different manner. The aim is
not just to estimate the cloud impact, but also to investigate to which degree
the cloud impact can be removed, i.e.\ to make a cloud correction. Further, in
this report only schemes that can be based directly on AWS data will be
considered and versions involving ``B-O tests'' are left for possible future
studies.
%On the other hand, cloud correction of all AWS 183\,GHz channels are
%investigated. Another important difference is that our simulations aim to be a
%random sample of real situations, while the simulations of
%\citet{rekha2012potential} have a strong over-representation of cloudy
%cases.

@@

The selected threshold value is towards the high side of the ones considered by 
\citet{rekha2012potential}. A lower value improves the removal of ``cloudy'' cases,
but the fraction of incorrectly removed ``clear'' cases increases quickly. For
example, a threshold of 3\,K decreases the miss-classification of ``cloudy''
cases to 0.6\%, but increases the miss-classification for ``clear'' cases to 77\%.
If 183\,$\pm$7\,GHz is classified as cloudy, we assume that also the data from
the other 183\,GHz channels are rejected.

@@

For simplicity, the frequency variation of all channel responses is assumed to
be rectangular. This selection shall not be interpreted as any opinion on the
optimal shape of these responses; a significant deviation from a rectangular
shape should be of no concern as long as the actual shape is well
characterised.

@@

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher over-representation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresented in the results.

\section{Overview of the 183, 229 and 325\,GHz bands}
\label{sec:overview}
% 
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$ (deviation from nadir). No hydrometeors are included. For simpler
interpretation of the results, the reflectivity is set to have no frequency
variation, i.e.\ the same value is applied for all bands. The reflectivity is
varied between 0 and 0.5 (these fixed values are only applied in this section,
the bulk simulations are using TESSEM and TELSEM for setting the surface
properties). In the figures covering transmissivities and Jacobians, the
specifications of ICI is applied for 325\,GHz channels
(Table~\ref{tab:fixed:chs}).

@@

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a three 325\,GHz channels option (three-a). The
    values in the three last columns is the 1$\sigma$ noise level according to
    Eq.~\ref{eq:noise}, for $T_a=300$\,K and stated $T_r$ }
  \label{tab:chs:prel3}
\end{table}

@@

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-42  & 325.15$\pm$3.30 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{The second three channel suggestion (three-b).}
  \label{tab:chs:3b}
\end{table}

@@

\begin{figure}[!b]
	\centering
	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
      against cloud impact in AWS-34. Red and green colour represent the clear
      and cloudy cases respectively in the simulation dataset. The black curve
      represents the line of best fit (of green points) as a third order
      polynomial. The blue vertical line represents the correction threshold,
      $x_{cs}$, for $dtb_{cs} =$ 0.2\,K. }
	\label{fig:fit:c34-42}
\end{figure}
%

@@

Figure~\ref{fig:correction:c34-42:thinned} shows the deviation of the uncorrected and
corrected measurements to their noise-free clear-sky values for the thinned dataset. The results from \cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to allow a more direct comparison of our
approach with \cite{rekha2012potential}, we also include the
dataset, ``Filtered'', where all cloudy cases are rejected. Apart from the fit
based cloudy classification, it is also assumed that cases with $Tb2-Tb1 < $
-15\,K are ``too-cloudy'' and are rejected.  To analyse the sensitivity of our scheme to noise threshold, as discussed in the previous section, results from two different values of $dtb_{cs}$ are shown. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
($x_{cs}$) is calculated using Eq~\ref{eq:dtb}. Various metrics corresponding to
the Figure~\ref{fig:correction:c34-42:thinned} are shown in
Table~\ref{tab:correction:stats:34:42:thinned}.

@@

\subsection{QRNN model}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).

@@

\subsubsection{Training}
%  
\label{sec:qrnn:training}
\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$). Here QRNN is trained to predict clear-sky values for AWS-34 using four channels option of 325\,GHz}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz
channels using TBs measurements from all available channels of 325\,GHz. A
separate QRNN is used for each of the 183\,GHz channels. For example, to
predict clear-sky TBs from AWS-34, the training data is measurements from all
channels of 325\,GHz and measurements from the 183\,GHz to be predicted. We
assess the performance of the scheme using both three channel and four channel
options of 325\,GHz. Two suggestions for three channel option are described in
Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN
separately. Thus, for each channel of 183\,GHz, we have a set of three
predictions: one from four channel option, and two from the old and new
configurations of the three channel option. Further in the text, the old and
new three channel configurations are labelled as "three-a" and "three-b".

To develop the QRNN scheme, we use the same dataset as in the
simple scheme . Out of 125\,000 simulations, 90\% are used to train the model,
while the rest 10\% is used to evaluate the model's performance during
training. Presently we train QRNN for only nadir sensor viewing angle and the
receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the
input according to Eq.~\ref{eq:noise}, every time the training data are exposed
to the model. This ensures that the model is exposed to a new dataset on every
iteration. Before training, the input data is normalized with mean and standard
deviation.

@@

The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. For QRNN models presented here, we did not optimise the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 256 samples for all QRNN models.

@@

The distributions of the predicted clear-sky noise-free values for each of the
183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}. The simulated
clear-sky distributions are also plotted for reference. These results are from
the four channel option. The distributions show that QRNN is overall successful in
predicting the clear-sky cases. For all channels, the simulations and
predictions have a good agreement for the main peak of the distribution.
However, for AWS-32, AWS-33 and AWS-34, QRNN seems to predict slightly colder
TBs. These results give an indication of the behaviour of QRNN, but for a
detailed analysis of the prediction accuracy, we make a quantitative assessment
of the errors.

@@

For AWS-35 (Table~\ref{tab:qrnn:C35}), the four channels option has the best performance. The average bias in QRNN predictions (four) is only 0.04\,K in comparison to -0.42\,K for the measurements. Option ``three-b'' has lower skewness than option four, but the standard deviation is higher. It is interesting to note that the standard deviation in all three predicted datasets is always lower than noise. Similar results are also seen for AWS-36 (Table~\ref{tab:qrnn:C36}). The four channels combination reduces the average bias from -0.269\,K to 0.056\,K and the standard deviation from 2.059\,K to 0.779\,K. Also for this channel, the spread of the predictions is narrower than noise.

@@

When trained with AWS-4X, the predictions are not very successful in
alleviating the cloud impact. Although, the error standard deviation of the
predicted dataset is lower, a large negative skewness (-4.085) indicates
significantly high uncorrected cloud impact. On the other hand, QRNN
predictions trained with 325\,GHz data are also not completely cloud free, but
have a slightly better accuracy. The error standard deviation for the four
channels option is 0.878\,K.
Clearly, without additional information, QRNN cannot learn to predict cloud
free values for AWS-32. As already seen in simple correction scheme, AWS-4X is
not sufficient enough to characterise the effect of hydrometeors in AWS-32.

@@

\section{Degrees of freedom}
%
An information content analysis is made by estimating the degrees of freedom
(DoF) of the simulated measurements. The analysis is similar to the one
described by \citet{eriksson:towar:20} for ICI.

@@

\begin{equation}
\mathbf{S_y = E \Lambda E^T} 
\end{equation}
Similarly, the uncertainty due to thermal noise is
\begin{equation}
\mathbf{S_{\Lambda} = E S_{\epsilon} E^T }
\end{equation}
where, $\mathbf{S_{\epsilon}}$ is a diagonal matrix with NE$\Delta$T$^2$ as
diagonal elements. The DoF is the number of diagonal elements of
$\mathbf{\Lambda}$ greater than the $\mathbf{S_\Lambda}$. For further details
see \citet{eriksson:towar:20}.

To calculate the DoF, the ensemble of simulations from 89\,GHz, 166\,GHz,
183\,GHz are used along with 229\,GHz or 325\,GHz. In order to compare the DoF
for cloudy and clear cases, we divide the database into three parts: ``all'',
``clear'' and ``cloudy'. All cases with cloud impact greater than 1\,K in any
of the 183\,GHz channels are classified as ``cloudy'', otherwise they are
classified as ``clear''. With this criteria, out of total 125460 cases, 12905
are classified as cloudy.

As example, Fig~\ref{fig:DoF:clear:1200K} shows the ratio of
$\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.
The DoF below is an interpolation between the last index having a ratio above
one and next index.

\subsection{DoFs for nominal IF range}

At this point we got feedback from Omnisys that also channel option 3b is
technically challenging. In short, it is significantly more difficult to
implement a 3\,GHz wide channel at an IF of 3.3\,GHz (AWS-42) than compared to
at 6.5\,GHz (AWS-41). To decrease the ratio between channel widths and centre
IF, a third three channel option was formulated (Table~\ref{tab:chs:3c}) that
is below denoted as three c. This option uses the same IF range as the
previously suggested ones.

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.25 & 3500  & 0.54 & 0.76 & 0.98\\
    AWS-42  & 325.15$\pm$3.05 & 2500  & 0.64 & 0.90 & 1.16\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{The third three channel suggestion (three-c).}
  \label{tab:chs:3c}
\end{table}

Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are
considered. For $T_r$ = 1200\,K, the DoF from all four options is around 8,
however, increase in receiver noise leads to a loss in the DoF.
Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for
clear-sky and cloudy cases respectively. For clear-sky situations, the DoFs are
about 77. With increase in $T_r$, the DoF are degraded. For $T_r$ = 2400\,K, we
have only 5 DoF for option three-a and 4.8 for both option three-b/c and 4.9
for option four. On the other hand, the presence of clouds increases the DoF
significantly. For all three options, we have DoF close to 9. Increase in noise
has a lower effect on the DoF for cloudy cases.

The DoF values should not be interpreted to strongly. There appears to be some
``noise'' in the DoF, especially for higher noise. For example, in
Table~\ref{tab:DoF:all} all the options have fairly similar DoF for
$T_r=1800$\,K while for $T_r=2400$\,K there are considerable differences. This
shift when going $T_r=2400$\,K is not observed in the two other tables. Having
this in mind, it seems that options three b and c give very similar DoF. If
something, option three-c seems slightly better. The four channel option
obtains somewhat lower DoF than the three channel ones.

@@

\subsection{Impact of extending the IF range}
%
As a basic investigation of the impact of changing the width of the IF range, a
version of the four channel option was considered, denoted as four-b. It was
modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
extension, only the edge channels were changed. That is, the revised AWS-41 and
have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
are found in Table~\ref{tab:DoF:4b}.
